---
title: "gtsummary in quarto"
format: 
  html:
    theme: sketchy
execute:
  echo: True 
---

**Information about the data**: 

The NLSY79 Cohort is a longitudinal project that follows the lives of a sample of American youth born between 1957-64. The cohort originally included 12,686 respondents ages 14-22 when first interviewed in 1979; after two subsamples were dropped, 9,964 respondents remain in the eligible samples. Data are now available from Round 1 (1979 survey year) to Round 29 (2020 survey year).

Exercise: I don’t like seeing the output from the first chunk, where the packages are loaded. Use an option that makes it so that we don’t see this chunk’s output.

```{r}
#| warning: false
#| message: false

library(tidyverse)
library(gtsummary)
nlsy_cols <- c("glasses", "eyesight", "sleep_wkdy", "sleep_wknd", 
               "id", "nsibs", "samp", "race_eth", "sex", "region", 
               "income", "res_1980", "res_2002", "age_bir")
nlsy <- read_csv(here::here("data", "raw", "nlsy.csv"), 
                 na = c("-1", "-2", "-3", "-4", "-5", "-998"),
                 skip = 1, col_names = nlsy_cols) |> 
  mutate(region_cat = factor(region, labels = c("Northeast", "North Central", "South", "West")),
         sex_cat = factor(sex, labels = c("Male", "Female")),
         race_eth_cat = factor(race_eth, labels = c("Hispanic", "Black", "Non-Black, Non-Hispanic")),
         eyesight_cat = factor(eyesight, labels = c("Excellent", "Very good", "Good", "Fair", "Poor")),
         glasses_cat = factor(glasses, labels = c("No", "Yes"))) 
```

# Customization of `tbl_summary()`

```{r}
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir))
```

```{r}
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir),
  label = list(
    race_eth_cat ~ "Race/ethnicity",
    region_cat ~ "Region",
    eyesight_cat ~ "Eyesight",
    glasses ~ "Wears glasses",
    age_bir ~ "Age at first birth"
  ),
  missing_text = "Missing")
```

Let’s not print the code from creating the tables. Using an option for the whole document, make it so that we don’t see the code from any of the chunks.

We'll add this: execute: eval: false echo: false

to the yaml section of the doc

For this next chunk

```{r}
#| label: Last Table

#| error: true
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir))
```

Choose a table to label and caption, and then write a sentence that cross-references it (e.g., Table 1 shows the descriptive statistics)


```{r}
#| label: tbl-one
#| tbl-cap: "This is a great table"
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir))



```

@tbl-one shows the descriptive statistics

#Means 

```{r}
#| echo: false
mean(nlsy$sleep_wknd, na.rm = TRUE)


```

```{r}
Avg_Wknd_Sleep <- mean(nlsy$sleep_wknd, na.rm = TRUE)
```

The average hours of sleep on weekends is `r Avg_Wknd_Sleep`

The average hours of sleep on weekends is `r mean(nlsy$sleep_wknd, na.rm = TRUE)`



#Medians
```{r}
#| echo: false
median(nlsy$sleep_wknd, na.rm = TRUE)


```

```{r}
Median_Wknd_Sleep <- median(nlsy$sleep_wknd, na.rm = TRUE)
```

The median number of hours of sleep on weekends is `r Median_Wknd_Sleep`

The median number of hours of sleep on weekends is `r median(nlsy$sleep_wknd, na.rm = TRUE)`

#Exercises part 2

```{r}

#| label: tbl-descr
#| tbl-cap: "Descriptive statistics"
#| output-location: slide
table1ppt <- tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir)) |> 
  add_overall(last = TRUE)
table1ppt


inline_text(table1ppt, variable = "age_bir", column = "stat_1")

```
The median (IQR) age of the male participants at the birth of their first child is `r inline_text(table1ppt, variable = "age_bir", column = "stat_1")`

Edit or create a new table that has the median hours of sleep on weekends in it (in the overall sample).

From that table, pull out the that value and include in the text using inline_text().
```{r}

#| label: tbl-descr
#| tbl-cap: "Descriptive statistics"
table1ppt <- tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir, sleep_wknd)) |> 
  add_overall(last = TRUE)
table1ppt

med_wkndsleep <- inline_text(table1ppt, variable = "sleep_wknd", column = "stat_0")

# for columns, overall column is stat_0 and then starts at 1 from left side

```

The median hours and IQR of sleep on weekends for the overall sample is `r inline_text(table1ppt, variable = "sleep_wknd", column = "stat_0")` hours.

The median hours and IQR of sleep on weekends for the overall sample is `r med_wkndsleep` hours.

